%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{dashrule}
\usepackage{ifthen}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[3][]{
  \item\small{
    \textbf{#2}{\ifthenelse{\equal{#3}{}}{}{:\\#3} \vspace{-2pt}}{\begin{flushright}\href{#1}{#1}\end{flushright}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://morteza-karimi.ir/}{\Large Morteza Karimi}} & Email : \href{mailto:me@morteza-karimi.ir}{me@morteza-karimi.ir}\\
  \href{https://morteza-karimi.ir/}{https://morteza-karimi.ir} & Mobile : +98-921-635-1266 \\
  DOB: 17/06/1994& Marital status: married\\
  Location: Shahrood, Iran
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shahrood University of Technology}{Shahrood, IR}
      {Master of Science in Artificial Intelligence; GPA: 3.77 (16.46/20)}{Sep. 2017 - Present}
      \vspace{1pt}\\
      \small{\textbf{Thesis Title:} Face re-identification using capsule neural network }
    \resumeSubheading
      {Khayyam University of Mashhad}{Mashhad, IR}
      {Bachelor of Engineering in Software Engineering; GPA: 3.17 (15.47/20)}{Sep. 2012 - July. 2017}
  \resumeSubHeadingListEnd

%-----------Artificial Intelligence-----------------
\section{Artificial Intelligence Experience}
\resumeSubHeadingListStart
\item{
	\textbf{Count the number and calculate size of fluid droplets and design a predictive system to calculate output droplet size}{:In this project, using the Python programming language, the number and size of the output droplets were identified and calculated in the laboratory system. Then, using the obtained database, the deep network prediction model was designed so that the input parameters can be predicted by the number and size of droplets.}
	\hfill
}
\item{
	\textbf{Implementation of oil and water droplet separation project}
	{: In this project, using MATLAB programming, separation and droplet counting were done automatically using image processing topics.}
	\hfill
}
\item{
	\textbf{Face Detection using deep learning}
	{: The project was designed with the help of existing methods for deep-seated facial recognition.}
}
\item{
	\textbf{Face tracking in video}
	{: In this project, using the Python programming language by using the OpenCV library, the tracker was designed to track face in the video.}
}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{http://zagstudio.ir/}{ZAG STUDIO}}
		      {Sabzevar, IR}		
      {BackEnd Web Developer}		
      {Sep. 2017 - Jan. 2019}		
      \resumeItemListStart
      	\resumeItem[http://portal.kamaposter.com]{Kama Poster Internal Portal}{Develop based on Yii2 Framework}
      	\resumeItem[http://bimehasiakarimi.com]{Asia Insurance Branch of Sabzevar Internal Portal}{Develop based on Yii2 Framework}
      	\resumeItem[http://bomaa.ir/]{bomaa Website}{Develop based on Yii2 Framework}
        \resumeItem[https://shokufa.org]{Shokufa Website}{Develop based on Yii2 Framework}
        \resumeItem[http://rabaze.com]{Rabaze Website}{Develop based on Laravel Framework}
      \resumeItemListEnd

      \hdashrule{\fill}{1pt}{1pt}
      
    \resumeSubheading{Khayyam University of Mashhad}{Mashhad, IR}{Web Developer}{Aug. 2014 - July. 2017}
      \resumeItemListStart
        \resumeItem[http://ce.khayyam.ac.ir]
       {Website of the Computer Engineering Society of Khayyam University}
        {Develop based on Yii2 Framework and Node.js Frameworks}
        \resumeItem
        {Cultural Affairs website of Khayyam University of Mashhad}
        {Develop based on Yii2 Framework}
        
      \resumeItemListEnd
      
      \hdashrule{\fill}{1pt}{1pt}
      
    \resumeSubheading{Other Projects}{Sabzevar, IR}{Software Engineer}{Feb. 2013 - Present}
      \resumeItemListStart
        \resumeItem
        [https://promac.ir]{Website of Promac Co.}{Develop based on Yii2 Framework}
        \resumeItem
        [https://github.com/mortezakarimi/gentelella-rtl]
        {Create Right to Left template based on Gentelella them}
        {Open source bootstrap3 template}
        
        \resumeItem
        [https://valencia.ir]{Valencia fan club website in Iran}{Develop based on Yii Framework}
        \resumeItem
        [http://a-rastegari.org]{Charity Foundation "Rastegari" website}{Develop based on Yii Framework}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: PHP, Python, Javascript, SQL, Matlab, C++, HTML, CSS, SCSS, TypeScript}
      \hfill
      }
    \item{
      \textbf{Web Frameworks}{: Yii2, Laravel, Yii, Bootstrap, JQuery, VueJs, Angular}
      \hfill
      }
    \item{
      \textbf{Python library}{: Tensorflow, Numpy, Keras, Pandas, OpenCV}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
