%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Team Lead \& Full Stack Developer} % Job title
    {Taban Nova (Trium Novem)} % Organization
    {Berlin, Germany (Remote)} % Location
    {\shortmonthname[08]. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 3 developers in building an ERP platform for construction company project and employee management, resulting in a 30\% increase in operational efficiency.}
        \item {Developed a mobile application for employee work time management, improving time tracking accuracy by 95\% and reducing payroll processing time by 50\%.}
        \item {Converted complex Excel-based processes into a comprehensive ERP system, streamlining operations and increasing data accuracy by 80\%.}
        \item { Implemented Next.js and React.js for frontend development, reducing page load times by 40\% and improving user experience.}
        \item {Utilized NestJS and Node.js to create a robust backend infrastructure, increasing concurrent user capacity by 200\% and reducing server response time by 40\%.}
        \item {Integrated Jira for project management, improving team productivity by 25\% and reducing project delivery times by 20\%.}
        \item {Provided hands-on technical leadership, mentoring junior developers and increasing team's code quality scores by 35\%.}
        \item{Optimized database queries and implemented caching strategies, resulting in a 60\% reduction in API response times.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry
    {Full Stack Developer \& DevOps Engineer} % Job title
    {Bugloos} % Organization
    {Netherlands (Hybrid)} % Location
    {\shortmonthname[08]. 2019 - \shortmonthname[08]. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Progressed from Backend Developer to Full Stack Developer and Junior DevOps Engineer, demonstrating versatility and rapid skill acquisition.}
        \item {Spearheaded the adoption of Angular framework, reducing frontend development time by 40\% and improving overall project structure by implementing modular architecture and reusable components, resulting in a 30\% decrease in code duplication.}
        \item {Implemented microservice architecture using Docker and Ansible, increasing system scalability by 200\% and reducing deployment times from hours to minutes.}
        \item {Designed and implemented GitLab CI/CD pipelines, automating 80\% of repetitive daily tasks and improving release efficiency by 60\%.}
        \item {Optimized backend performance for e-commerce and portal projects, reducing query response times by 50\% and improving user experience.}
        \item {Mentored a team of 5 developers in Angular and DevOps best practices, resulting in a 30\% increase in team productivity and code quality.}
        \item{Modernized legacy systems by updating deprecated bundles and extensions, reducing system vulnerabilities by 70\% and improving overall stability.}
        \item {Engineered a new workflow system that increased release frequency by 100\% while maintaining high code quality standards.}
        \item{Utilized Symfony, PHP, MySQL, and Doctrine to develop robust backend solutions, handling a 300\% increase in concurrent users.}
        \item{Implemented Nginx and optimized server configurations, resulting in a 45\% improvement in application load times.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {HeyzhaCO} % Organization
    {Sabzevar, Iran} % Location
    {\shortmonthname[09]. 2017 - \shortmonthname[01]. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the development and optimization of multiple web applications using Laravel and Yii2 frameworks, resulting in a 33\% improvement in overall project performance.}
        \item {Debugged and resolved critical issues in existing Laravel-based website, reducing customer-reported bugs by 75\% and improving user satisfaction.}
        \item {Designed and implemented complex web portals, increasing the company's capacity to handle large-scale projects by 50\%.}
        \item {Introduced Yii2 framework to the company's tech stack, leading to a 40\% reduction in development time for new projects.}
        \item {Optimized database queries and implemented caching strategies, improving application response times by 60\%.}
        \item {Developed reusable code components, reducing future development time by 25\% and improving code maintainability.}
        \item{Collaborated with cross-functional teams to gather and implement business requirements, resulting in a 95\% client satisfaction rate.}
        \item{Mentored junior developers in best practices for Laravel and Yii2, improving team productivity by 30\%.}
        \item{Implemented automated testing procedures, reducing post-release bugs by 40\% and improving overall code quality.}
        \item{Contributed to the company's business growth, with web development projects increasing by 70\% during tenure.}
      \end{cvitems}
    }
    
    
    
    %---------------------------------------------------------
    \cventry
    {Back End Developer} % Job title
    {Khayyam University Of Mashhad} % Organization
    {Mashhad, Iran (Part-time during studies)} % Location
    {\shortmonthname[01]. 2015 - \shortmonthname[09]. 2017} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {Developed a real-time multiplayer Tic-Tac-Toe game using Node.js and Socket.io, integrating it with an iOS app.}
    		\item { Implemented WebSocket technology to enable real-time gameplay, reducing latency by 80\% compared to traditional HTTP requests.}
    		\item {Led the backend development of Khayyam University's Culture Center website, utilizing a hybrid Node.js and PHP architecture to optimize performance.}
    		\item {Designed and implemented RESTful APIs, improving data flow between frontend and backend.}
    		\item {Collaborated with a cross-functional team of 3 members, including designers and frontend developers, to deliver the Culture Center website on time and within budget.}
    		\item {Implemented user authentication and authorization systems, ensuring secure access for over 50 university students and staff.}
    		\item{Utilized Git for version control, improving team collaboration and reducing code conflicts by 70\%.}
    		\item{Received recognition from the university's IT department for exceptional problem-solving skills and innovative use of emerging technologies.}
    	\end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
